Survey: Modal Verification Patterns for Systems

### 2025-06-25 paper.tex
+

%\bibliography{references/paper}
\begin{document}
%
\title{Modal Verification Patterns for Systems}
%
%\titlerunning{RCU Types}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Ismail Kuru \orcidID{0000-0002-5796-2150} \and
Colin S. Gordon \orcidID{0000-0002-9012-4490}}
%%%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{Kuru and Gordon}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Drexel University \\ %\and
%%%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{\{ik335,csgordon\}@drexel.edu}}%\\
%%%\url{http://www.springer.com/gp/computer-science/lncs} \and
%%%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%%%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution

@@

This choice trades off complexity against flexibility and scoping constraints.
Strongly nominalized elements track additional specifier/prover-visible book-keeping data.
But in exchange for carrying those identifiers of their context with them, 
strongly nominalized elements can be used together under any modality. For example, one can
use the StackRegion modality to talk about two different stack frames simultaneously for code
which accesses multiple stack frames: $\fbox{n} \; \ell \mapsto v \ast \fbox{n+1} \; \ell' \mapsto v'$.
Using a given strongly nominalized assertion element under different modalities for different
frames does not change its meaning. Likewise,  weak-memory specific modalities existentially quantify over other views, related to the ``current'' view (the one where
the current thread's assertions are evaluated), and evaluate a resource (an thread-local view of an address-value mapping) with respect to those other views. Although it looks like the pattern we see in the VMM case,
It is \emph{not}, however, an instance of hybrid logic, which is specifically demarcated by an assertion language where
\emph{assertions}, not their semantics, choose and name the evaluation points for modal assertions.
A hybrid extension of the aforementioned logics would include assertions which named specific views at which to evaluate
$P$, in the syntax of the assertion (e.g., $\Delta_\pi^v(P):=\lambda\_\ldotp (P\;v)$) rather than the 
$\Delta_\pi(P):= \lambda v\ldotp (\exists v_{rel}\ldotp \ownGhost{\pi}{\mathsf{RelV}(v_{rel})\;v} \ast (P\;v_{rel})))$ actually used.
Note the hybrid version takes the place to evaluate $P$ as a parameter, and therefore allows the \emph{derived} (modal) logic to explicitly
reason in terms of evaluation points, rather than hiding all points of evaluation in the internal definitions of modalities.

>>>>

%\bibliography{references/paper}
\begin{document}
%
\title{Survey: Modal Verification Patterns for Systems}
%
%\titlerunning{RCU Types}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{Ismail Kuru \orcidID{0000-0002-5796-2150} \and
%Colin S. Gordon \orcidID{0000-0002-9012-4490}}
%%%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
%\authorrunning{Kuru and Gordon}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Drexel University \\ %\and
%%%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
%\email{\{ik335,csgordon\}@drexel.edu}}%\\
%%%\url{http://www.springer.com/gp/computer-science/lncs} \and
%%%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%%%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution

@@

This choice trades off complexity against flexibility and scoping constraints.
Strongly nominalized elements track additional specifier/prover-visible book-keeping data.
But in exchange for carrying those identifiers of their context with them, 
strongly nominalized elements can be used together under any modality. For example, one can
use the StackRegion modality to talk about two different stack frames simultaneously for code
which accesses multiple stack frames: $\fbox{n} \; \ell \mapsto v \ast \fbox{n+1} \; \ell' \mapsto v'$.
Using a given strongly nominalized assertion element under different modalities for different
frames does not change its meaning. Likewise,  weak-memory specific modalities existentially quantify over other views, related to the ``current'' view (the one where
the current thread's assertions are evaluated), and evaluate a resource (an thread-local view of an address-value mapping) with respect to those other views.
